---
title: "MSAI"
author: "Hui Peng"
date: '2024-11-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This package is used to prepare MS data for machine learning models:
requriements:
1. MS1 peak lists in the folder of 'peaklist'
2. Raw MS2 DIA data in the folder of 'data'
3. results folder to save results
4. the name of peak list documents should be matched to raw MS data

```{r, message=FALSE, warning=FALSE}
  rm(list=ls())
  install.packages("C:\\1Xiaoyun\\460K_Complete (MS1MS2)data processing procedure\\CODE\\STEP2\\MSAI\\R\\GetFrag.R")  
  library(MSAI)
  library(xcms)
  library(devtools)
  library(xlsx)
  library(ChemmineR)
  library(rcdk)
  library(MassSpecWavelet)
  library(Rcpp)
  library(RcppArmadillo)
  library(isopat)
  library(readxl)
  data(iso_list)
  #'set up the path
  path<-"C:\\1Xiaoyun\\460K_Complete (MS1MS2)data processing procedure\\CODE\\STEP2\\MSAI"
  DIAisowin<-4.5 ##window of DIa
  mz_tol<-4*10^(-6) ##MS tolerance
  RTwin<-10 #retention time window
  setwd(path)
```

Extracting MS2

```{r pressure, echo=FALSE}

myms2<-GetFrag(mz_tol,DIAisowin,RTwin)
```

Extracting two chiral LC peaks

Two chiral peaks are separated by retention time windows. MS2 fragments are
extracted for each window, but this function does not automatically assign R/S.
The MVP does not perform peak deconvolution. The `apex_rt` output is reported in
seconds because raw retention times are handled in seconds internally.

```{r chiral-ms2, eval=FALSE}

my_chiral_ms2<-GetChiralFrag(
  mz_tol = 0.00001,
  DIAisowin = 20,
  peak_a_rt_window = c(5.10, 5.35),
  peak_b_rt_window = c(5.70, 5.95),
  rt_unit = "min"
)
```
