---
title: "MSAI"
author: "Hui Peng"
date: '2024-11-29'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
This package is used to prepare MS data for machine learning models:

The current Python project is primarily an MS2 workflow: it extracts and
compares DIA-MS2 spectra for supplied `Peak1`/`Peak2` retention times. Automatic
MS1 peak picking is retained only as an experimental method-development
reference and is not required by the core MS2 analysis.

requriements:
1. MS1 peak lists in the folder of 'peaklist'
2. Raw MS2 DIA data in the folder of 'data'
3. results folder to save results
4. the name of peak list documents should be matched to raw MS data

```{r, message=FALSE, warning=FALSE}
  rm(list=ls())
  install.packages("C:\\1Xiaoyun\\460K_Complete (MS1MS2)data processing procedure\\CODE\\STEP2\\MSAI\\R\\GetFrag.R")  
  library(MSAI)
  library(xcms)
  library(devtools)
  library(xlsx)
  library(ChemmineR)
  library(rcdk)
  library(MassSpecWavelet)
  library(Rcpp)
  library(RcppArmadillo)
  library(isopat)
  library(readxl)
  data(iso_list)
  #'set up the path
  path<-"C:\\1Xiaoyun\\460K_Complete (MS1MS2)data processing procedure\\CODE\\STEP2\\MSAI"
  DIAisowin<-4.5 ##window of DIa
  mz_tol<-4*10^(-6) ##MS tolerance
  RTwin<-10 #retention time window
  setwd(path)
```

Extracting MS2

```{r pressure, echo=FALSE}

myms2<-GetFrag(mz_tol,DIAisowin,RTwin)
```

Extracting two chiral LC peaks

Two chiral peaks are separated by retention time windows. MS2 fragments are
extracted for each window, but this function does not automatically assign R/S.
The legacy R entry point does not perform the indexed consensus/deconvolution
implemented by the Python v2 workflow. The `apex_rt` output is reported in
seconds because raw retention times are handled in seconds internally.

```{r chiral-ms2, eval=FALSE}

my_chiral_ms2<-GetChiralFrag(
  mz_tol = 0.00001,
  DIAisowin = 20,
  peak_a_rt_window = c(5.10, 5.35),
  peak_b_rt_window = c(5.70, 5.95),
  rt_unit = "min"
)
```

## Recommended per-row peak-pair analysis

The supplied screening table contains a separate `Peak1` and `Peak2` retention
time for each compound, so one global pair of windows is not appropriate.  The
Python workflow reads `MZ`, `Peak1`, and `Peak2` per row, extracts both spectra,
and adds cosine similarity, exclusive matched-ion count, explained intensity,
and a conservative candidate classification.

```{powershell, eval=FALSE}
python MSAI\python\get_chiral_frag.py `
  --peaklist MSAI\peaklist\merged_result_IG_EASMSV1.csv `
  --raw MSAI\data\IG_STD500nM_EASMSV1_2.mzXML `
  --output MSAI\results\merged_result_IG_EASMSV1_chiral_MS2_similarity.csv
```

The default candidate criterion is cosine >= 0.7, at least six matched product
ions, and at least 50% explained intensity in both spectra.  This identifies a
candidate enantiomer pair only.  Absolute R/S assignment still requires
authentic enantiopure standards analyzed with the same chiral LC method.

The Python v2 implementation also provides automatic MS1 peak picking,
spectral-entropy similarity, real isolation-window parsing, calibrated
threshold profiles, manifest-based A01-A11 batch processing, resume support,
and run metadata. See `README.md` for the current commands and validation
results; this R Markdown section is retained for legacy package users.
